---
title: "Testing implementation in `semTools::compRelSEM()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

```{r load-pkg, message = FALSE}
library(tidyverse)
library(lavaan)
library(semTools)
```

## Configural Model in [Lai (2021)](https://doi.org/10.1037/met0000287)

### Data Import

```{r timss_usa}
timss_usa <- haven::read_sav("../../timss/data/asgUSAm4.sav") %>%
    select(
        IDCNTRY, IDSCHOOL,
        AS4MAMOR, AS4MAENJ, AS4MALIK, AS4MABOR
    ) %>%
    drop_na() %>%
    mutate(AS4MABORr = 5 - AS4MABOR)
```

### Comparison

```{r}
# Note: need to use the same name for the factors at level-1 and level-2
mcfa11 <- 
   'level: 1
     f1 =~ NA * AS4MAMOR + l1 * AS4MAMOR + l2 * AS4MAENJ + l3 * AS4MALIK + l4 * AS4MABORr
     AS4MAMOR ~~ ev1w * AS4MAMOR
     AS4MAENJ ~~ ev2w * AS4MAENJ
     AS4MALIK ~~ ev3w * AS4MALIK
     AS4MABORr ~~ ev4w * AS4MABORr
     f1 ~~ 1 * f1
   level: 2
     f1 =~ NA * AS4MAMOR + l1 * AS4MAMOR + l2 * AS4MAENJ + l3 * AS4MALIK + l4 * AS4MABORr
     # fixed residual variances
     AS4MAMOR ~~ ev1b * AS4MAMOR
     AS4MAENJ ~~ 0 * AS4MAENJ
     AS4MALIK ~~ ev3b * AS4MALIK
     AS4MABORr ~~ ev4b * AS4MABORr
     f1 ~~ vf1b * f1
   # tilde omega values:
   tilomgb := (l1 + l2 + l3 + l4)^2 * vf1b /
              ((l1 + l2 + l3 + l4)^2 * vf1b + ev1b + 0 + ev3b + ev4b)
   tilomgw := (l1 + l2 + l3 + l4)^2 * 1 /
              ((l1 + l2 + l3 + l4)^2 * 1 + ev1w + ev2w + ev3w + ev4w)
   # score reliability:
   omg2l := (l1 + l2 + l3 + l4)^2 * (1 + vf1b) /
            ((l1 + l2 + l3 + l4)^2 * (1 + vf1b) + 
             ev1b + 0 + ev3b + ev4b + ev1w + ev2w + ev3w + ev4w)
   omgb := (l1 + l2 + l3 + l4)^2 * vf1b /
           ((l1 + l2 + l3 + l4)^2 * vf1b + ev1b + 0 + ev3b + ev4b + 
            (ev1w + ev2w + ev3w + ev4w + (l1 + l2 + l3 + l4)^2) / 25.1)'

mcfa11_fit <- cfa(mcfa11, data = timss_usa, cluster = "IDSCHOOL")
summary(mcfa11_fit)
```

```{r}
coef(mcfa11_fit, type = "user")[c("tilomgw", "omg2l", "omgb")]
```

```{r}
comp_rel <- compRelSEM(mcfa11_fit,
    obs.var = FALSE,
    config = c("f1"), shared = "f1"
)
comp_rel
```

Discrepancy in the between reliability likely due to rounding error in the harmonic mean of cluster sizes, in which case `compRelSEM()` should be more accurate.

## Saturated Within-Cluster Model

### Data Import

```{r timss_eng}
timss15_eng <- haven::read_sav("../../timss/data/MSGUSAM3.sav") %>%
  select(
    IDCNTRY, IDSCHOOL, IDCLASS,
    MSBM18A, MSBM18B, MSBM18C, MSBM18H, MSBM18I, MSBM18M
  )
```

### Comparison

```{r}
mcfas1 <- 
  'level: 1
     MSBM18A ~~ c11w * MSBM18A + c12w * MSBM18B + c13w * MSBM18C + 
                c14w * MSBM18H + c15w * MSBM18I + c16w * MSBM18M
     MSBM18B ~~ c22w * MSBM18B + c23w * MSBM18C + c24w * MSBM18H + 
                c25w * MSBM18I + c26w * MSBM18M
     MSBM18C ~~ c33w * MSBM18C + c34w * MSBM18H + c35w * MSBM18I + 
                c36w * MSBM18M
     MSBM18H ~~ c44w * MSBM18H + c45w * MSBM18I + c46w * MSBM18M
     MSBM18I ~~ c55w * MSBM18I + c56w * MSBM18M
     MSBM18M ~~ c66w * MSBM18M
   level: 2
     f1b =~ NA * MSBM18A + l1 * MSBM18A + l2 * MSBM18B + l3 * MSBM18C + 
            l4 * MSBM18H + l5 * MSBM18I + l6 * MSBM18M
     # fixed residual variances
     MSBM18A ~~ ev1b * MSBM18A
     MSBM18B ~~ ev2b * MSBM18B
     MSBM18C ~~ ev3b * MSBM18C
     MSBM18H ~~ ev4b * MSBM18H
     MSBM18I ~~ ev5b * MSBM18I
     MSBM18M ~~ ev6b * MSBM18M
     f1b ~~ 1 * f1b
   # score reliability:
   omgb := (l1 + l2 + l3 + l4 + l5 + l6)^2 /
              ((l1 + l2 + l3 + l4 + l5 + l6)^2 + 
               ev1b + ev2b + ev3b + ev4b + ev5b + ev6b + 
           (c11w + c22w + c33w + c44w + c55w + c66w + 
            2 * (c12w + c13w + c14w + c15w + c16w + 
                 c23w + c24w + c25w + c26w + 
                 c34w + c35w + c36w + c45w + c46w + c56w)) / 9.15)'
mcfas1_fit <- cfa(mcfas1, data = timss15_eng, cluster = "IDCLASS")
summary(mcfas1_fit)
```

```{r}
coef(mcfas1_fit, type = "user")["omgb"]
```

```{r}
compRelSEM(mcfas1_fit,
    obs.var = FALSE,
    shared = "f1b"
)
```

The documentation of `compRelSEM()` recommends not using a saturated within-cluster model. Using such a model, the computation assumes the within-variance is zero, which overestimates the reliability.

## Simultaneous Shared-and-Configural Model

### Comparison

```{r}
mcfa11shared <- 
  'level: 1
     f1 =~ NA * MSBM18A + l1 * MSBM18A + l2 * MSBM18B + l3 * MSBM18C + 
            l4 * MSBM18H + l5 * MSBM18I + l6 * MSBM18M
     MSBM18A ~~ ev1w * MSBM18A
     MSBM18B ~~ ev2w * MSBM18B
     MSBM18C ~~ ev3w * MSBM18C
     MSBM18H ~~ ev4w * MSBM18H
     MSBM18I ~~ ev5w * MSBM18I
     MSBM18M ~~ ev6w * MSBM18M
     f1 ~~ 1 * f1
   level: 2
     f1 =~ NA * MSBM18A + l1 * MSBM18A + l2 * MSBM18B + l3 * MSBM18C + 
            l4 * MSBM18H + l5 * MSBM18I + l6 * MSBM18M
     f1bs =~ MSBM18A + l2s * MSBM18B + l3s * MSBM18C + 
             l4s * MSBM18H + l5s * MSBM18I + l6s * MSBM18M
     # fixed residual variances
     MSBM18A ~~ ev1b * MSBM18A
     MSBM18B ~~ ev2b * MSBM18B
     MSBM18C ~~ ev3b * MSBM18C
     MSBM18H ~~ ev4b * MSBM18H
     MSBM18I ~~ ev5b * MSBM18I
     MSBM18M ~~ ev6b * MSBM18M
     f1 ~~ (.05 / (1 - .05)) * f1
     f1bs ~~ v1bs * f1bs
     f1 ~~ 0 * f1bs
   # score reliability:
   omgbs := (1 + l2s + l3s + l4s + l5s + l6s)^2 * v1bs /
            ((l1 + l2 + l3 + l4 + l5 + l6)^2 * .05 / (1 - .05) + 
             (1 + l2s + l3s + l4s + l5s + l6s)^2 * v1bs + 
             ev1b + ev2b + ev3b + ev4b + ev5b + ev6b + 
             (ev1w + ev2w + ev3w + ev4w + ev5w + ev6w + 
              (l1 + l2 + l3 + l4 + l5 + l6)^2) / 9.15)'
mcfa11sh_fit <- cfa(mcfa11shared, data = timss15_eng, cluster = "IDCLASS")
summary(mcfa11sh_fit)
```

```{r}
# Reliability for shared construct
coef(mcfa11sh_fit, type = "user")["omgbs"]
```

```{r}
compRelSEM(mcfa11sh_fit,
    obs.var = FALSE,
    config = "f1",
    shared = c("f1", "f1bs")
)
```

The discrepancy is due to level-1 variances not included for the construct reliability of `f1bs`.

```{r}
par2 <- lavInspect(mcfa11sh_fit, what = "est")$IDCLASS
lam2 <- par2$lambda
phi2 <- par2$psi
theta2 <- par2$theta
sum_lam2 <- colSums(lam2)
# Common variance for f1 at between-level
comvar_f1 <- sum_lam2[1]^2 * phi2[1, 1]
# Common variance for f1bs at between-level
comvar_f1bs <- sum_lam2[2]^2 * phi2[2, 2]
c(comvar_f1, comvar_f1bs) / (sum(comvar_f1, comvar_f1bs, theta2))
```

Accounting for the level-1 variances:

```{r}
par1 <- lavInspect(mcfa11sh_fit, what = "est")$within
lam1 <- par1$lambda
phi1 <- par1$psi
theta1 <- par1$theta
sum_lam1 <- colSums(lam1)
# Common variance for f1 at within-level
comvar_f1w <- sum_lam1[1]^2 * phi1[1, 1]
# Add in the level-1 variances
c(comvar_f1, comvar_f1bs) /
  (sum(comvar_f1, comvar_f1bs, theta2) + sum(comvar_f1w, theta1) / 9.15)
```
